---
title: Peak Climbing Club New Members Survey
authors:
  - name: Neil Shephard
    affiliation: Peak Climbing Club
    roles: New Member Representative
    corresponding: true
bibliography: references.bib
---

## Overview

The [Peak Climbing Club][pcc] has conducted a [survey][survey] to review the current joining procedure to see if there
are any improvements that can be made to the process.

``` {r}
#| label: setup
#| eval: true
#| echo: false
require(tidyverse)
BASE_DIR <- getwd()
DATA_DIR <- paste0(BASE_DIR, "/data/")
CSV_DIR <- paste0(DATA_DIR, "csv/")

survey_file <- paste0(CSV_DIR, "survey.csv")
survey <- read_csv(survey_file)
```

``` {r}
#| label: clean
#| eval: false
#| echo: false
questions <- colnames(survey)
colnames(survey) <- c("timestamp",
    "find",
    "info",
    "info_suggestion",
    "indoor_find",
    "indoor_climb",
    "outdoor_find",
    "outdoor_climb",
    "climb_suggestion",
    "join",
    "join_reason",
    "improve",
    "other"
    )
```
## Responses

### How did you find out about the club?

``` {r}
#| label: finding
#| eval: true
#| echo: false

```

### How easy was it to find information on joining the Peak Climbing Club?

``` {r}
#| label: info
#| eval: true
#| echo: false

```

### As a prospective/new member how easy was it for you to find information on where and when the club was meeting?

``` {r}
#| label: where-when
#| eval: true
#| echo: false

```

### On the meets you attended at indoor walls how easy was it to find members of the Peak Climbing Club?

``` {r}
#| label: indoor-find
#| eval: true
#| echo: false

```

### On the meets you attended at indoor walls how easy was it to find someone to climb with?

``` {r}
#| label: indoor-climb
#| eval: true
#| echo: false

```

### On the meets you attended at outdoor crags how easy was it to find members of the Peak Climbing Club?

``` {r}
#| label: outdoor-find
#| eval: true
#| echo: false

```

### On the meets you attended at outdoor crags how easy was it find someone to climb with at outdoor crags?

``` {r}
#| label: outdoor-climb
#| eval: true
#| echo: false

```

### If you found it hard to find someone to climb with either indoors or at the crag do you have any suggestions as to how we might improve this?

``` {r}
#| label: join-reason
#| eval: true
#| echo: false

```

### Did you decide to join the Peak Climbing Club?

``` {r}
#| label: join
#| eval: true
#| echo: false

```


### Do you have any feedback about how the club could improve the joining process?

``` {r}
#| label: improve
#| eval: true
#| echo: false

```

### Is there anything else you would like to share with us about the process of joining the Peak Climbing Club?

``` {r}
#| label: other
#| eval: true
#| echo: false

```


[pcc]: https://www.peakclimbingclub.co.uk/
[quarto]: https://www.quarto.org/
[r]: https://www.r-project.org/
[report]: https://nshephard.dev/pcc-new-member-survey
[survey]: https://forms.gle/f5JWtnwqUiwh1hgg7
