---
title: Peak Climbing Club New Members Survey
authors:
  - name: Neil Shephard
    affiliation: Peak Climbing Club
    roles: New Member Representative
    corresponding: true
bibliography: references.bib
knitr:
  opts_chunk:
    collapse: true
---


{{< qrcode <https://org-roam.nshephard.dev/pcc-new-member-survey> qr1 width=400 height=400 >}}

## [org-roam.nshephard.dev/pcc-new-member-survey](https://org-roam.nshephard.dev/pcc-new-member-survey)

## Overview

The [Peak Climbing Club][pcc] has conducted a [survey][survey] to review the current joining procedure to see if there
are any improvements that can be made to the process.

``` {r}
#| label: setup
#| eval: true
#| echo: false
require(tidyverse)
library(plotly)
BASE_DIR <- getwd()
DATA_DIR <- paste0(BASE_DIR, "/data/")
CSV_DIR <- paste0(DATA_DIR, "csv/")

survey_file <- paste0(CSV_DIR, "survey.csv")
survey <- read_csv(survey_file)

new_member_file <- paste0(CSV_DIR, "mailing_list.csv")
new_member <- read_csv(new_member_file)

```

``` {r}
#| label: clean
#| eval: true
#| echo: false
col_names <- c("timestamp",
    "find",
    "info",
    "where_when",
    "improve_where_when",
    "indoor_find",
    "indoor_climb",
    "outdoor_find",
    "outdoor_climb",
    "climb_suggestion",
    "join",
    "join_reason",
    "improve",
    "other")
questions <- colnames(survey)
names(questions) <- col_names
colnames(survey) <- col_names
## TODO - Convert to factors
levels = c("1", "2", "3", "4", "5")
labels = c("Very Easy", "2", "3", "4", "Very Hard")
survey <- survey |>
    dplyr::mutate(find = factor(find,
                                levels=c("Search on Internet", "Word of Mouth/Friend", "BMC", "Other"),
                                labels=c("Search on Internet", "Word of Mouth/Friend", "BMC", "Other")),
                  info = factor(info,
                                levels=levels,
                                labels=labels),
                  where_when = factor(where_when,
                                      levels=levels,
                                      labels=labels),
                  indoor_find = factor(indoor_find,
                                       levels=levels,
                                       labels=labels),
                  indoor_climb = factor(indoor_climb,
                                        levels=levels,
                                        labels=labels),
                  outdoor_find = factor(outdoor_find,
                                        levels=levels,
                                        labels=labels),
                  outdoor_climb = factor(outdoor_climb,
                                         levels=levels,
                                         labels=labels),
                  join = factor(join,
                                levels=c("No", "Not yet but I intend to", "Yes"),
                                labels=c("No", "Not yet but I intend to", "Yes")))
new_member <- new_member |>
    dplyr::mutate(gender = factor(gender,
                                levels=c("male", "female"),
                                labels=c("male", "female")))


```

## Methods

This report was generated using [Quarto][quarto] and the [R][r] statistical programming language and is hosted on GitHub
Pages.

## Applications

### Gender

Based on names extracted from emails, not necessarily 100% accurate

``` {r}
#| label: gender
#| eval: true
#| echo: false
#| output: true
new_member |> ggplot2::ggplot(aes(gender, fill=gender)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["find"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

```

### Date of Contact

**TODO**
``` {r}
#| label: date-of-contact
#| eval: true
#| echo: false
#| output: true
## new_member |> ggplot2::ggplot(aes(gender, fill=gender)) +
##   ggplot2::geom_bar() +
##   ggplot2::scale_x_discrete(drop = FALSE) +
##   ## ggplot2::ggtitle(questions[["find"]]) +
##   ggplot2::ggtitle("") +
##   ggplot2::xlab("") +
##   ggplot2::ylab("N") +
##   ggplot2::theme_minimal() +
##   ggplot2::theme(legend.position = "none")

```

## Responses

### How did you find out about the club?

``` {r}
#| label: finding
#| eval: true
#| echo: false
#| output: true
survey |> ggplot2::ggplot(aes(find, fill=find)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["find"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

```

### How easy was it to find information on joining the Peak Climbing Club?

``` {r}
#| label: info
#| eval: true
#| echo: false
#| output: true
survey |> ggplot2::ggplot(aes(info, fill=factor(info))) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["info"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

```

### As a prospective/new member how easy was it for you to find information on where and when the club was meeting?

``` {r}
#| label: where-when
#| eval: true
#| echo: false
#| output: true

survey |> ggplot2::ggplot(aes(where_when, fill=where_when)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["where_when"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")


```

### On the meets you attended at indoor walls how easy was it to find members of the Peak Climbing Club?

``` {r}
#| label: indoor-find
#| eval: true
#| echo: false
#| output: true
survey |> ggplot2::ggplot(aes(indoor_find, fill=indoor_find)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["indoor_find"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")


```

### On the meets you attended at indoor walls how easy was it to find someone to climb with?

``` {r}
#| label: indoor-climb
#| eval: true
#| echo: false
#| output: true
survey |> ggplot2::ggplot(aes(indoor_climb, fill=indoor_climb)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["indoor_climb"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")


```

### On the meets you attended at outdoor crags how easy was it to find members of the Peak Climbing Club?

``` {r}
#| label: outdoor-find
#| eval: true
#| echo: false
#| output: true
survey |> ggplot2::ggplot(aes(outdoor_find, fill=outdoor_find)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["outdoor_find"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

```

### On the meets you attended at outdoor crags how easy was it find someone to climb with at outdoor crags?

``` {r}
#| label: outdoor-climb
#| eval: true
#| echo: false
#| output: true
survey |> ggplot2::ggplot(aes(outdoor_climb, fill=outdoor_climb)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["outdoor_climb"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

```

### If you found it hard to find someone to climb with either indoors or at the crag do you have any suggestions as to how we might improve this?

``` {r}
#| label: join-reason
#| eval: true
#| echo: false
#| output: true
survey |> dplyr::select(join_reason) |>
  dplyr::filter(!is.na(join_reason)) |>
  knitr::kable(title="Comments...")

```

### Did you decide to join the Peak Climbing Club?

``` {r}
#| label: join
#| eval: true
#| echo: false
#| output: true
survey |> ggplot2::ggplot(aes(join, fill=join)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ## ggplot2::ggtitle(questions[["join"]]) +
  ggplot2::ggtitle("") +
  ggplot2::xlab("") +
  ggplot2::ylab("N") +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

```


### Do you have any feedback about how the club could improve the joining process?

``` {r}
#| label: improve
#| eval: true
#| echo: false
#| output: true
survey |> dplyr::select(improve) |>
  dplyr::filter(!is.na(improve)) |>
  knitr::kable(title="Comments...")

```

### Is there anything else you would like to share with us about the process of joining the Peak Climbing Club?

``` {r}
#| label: other
#| eval: true
#| echo: false
#| output: true
survey |> dplyr::select(other) |>
  dplyr::filter(!is.na(other)) |>
  knitr::kable(title="Comments...")

```


[pcc]: https://www.peakclimbingclub.co.uk/
[quarto]: https://www.quarto.org/
[r]: https://www.r-project.org/
[report]: https://nshephard.dev/pcc-new-member-survey
[survey]: https://forms.gle/f5JWtnwqUiwh1hgg7
